SAT Competition 2020\tnoteref{title}

### 2021-01-31 paper/main.tex
Section 4

The rest of this article is organized as follows. 
We start by providing an overview on the competition, including details on and motivations for the several
competition tracks, the rules and other technical requirements of the competition, the ranking schemes used
in evaluating the competing solvers, 
and the computing environments used for executing the competition
(Section~\ref{sec:overview}).
We then provide an overview of the benchmark sets used in evaluating the solvers, including their origins and the selection
process used for constructing the sets (Section~\ref{sec:instances}).
In Section~\ref{sec:results} we provide an overview of the competition results together with  a survey on the
the solving strategies implemented distinctly in  top-ranking  solvers. 
Going considerably beyond the plain competition rankings, we provide more in-depth analysis of the competition 
data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
of individual solvers to the ``virtual best solver'' and 
portfolios constructed from the competing solvers,  (Section~\ref{sec:analysis}.
The article is concluded with future prospects in Section~\ref{sec:conclusion}.
\todo{Need to decide on final structure regardign the results overview and analysis}

@@

Some interesting results were observed in the 2020 SAT Competition.
Four Main track solvers (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alliup-trial}, and \solver{CMS-ccnr-lsids}) 
performed significantly better compared to the others, see Figure~\ref{main:all} and Table~\ref{tab:results}.
These four top solvers all have a different code base, which is rare. In recent competitions, top solvers were much closer together.
The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
\solver{Relaxed-newTech} solved more instances within the 2000 seconds limit.
The third place, based on the PAR-2 score, was for \solver{CMS-ccnr-lsids}. It solved two fewer instances
compared to \solver{CaDiCaL-alliup-trial}, but solved various formulas much more efficiently. 
Since the SAT Competition started to rank based on PAR-2 score, such cases have been observed several times.

@@

The solver performances on unsatisfiable formulas was much closer,
see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
performed significantly better compared to all other participants. It is therefore not surprising
that the VBS is reasonably close to \solver{Kissat-unsat}. \solver{Kissat} is a new solver,
which has been implemented in C, while most solvers are implemented in C++. Further 
details about \solver{Kissat} are described in Section~\ref{sec:kissat}.
The solvers \solver{CaDiCaL-trial}
and \solver{f2trc-s} won the second, respectively, third place in the Main UNSAT track.

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
\label{main:all}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-SAT.pdf}
\caption{Performance of the top 10 solvers + VBS on Main track satisfiable benchmarks}
\label{main:sat}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-UNSAT.pdf}
\caption{Performance of the top 10 solvers + VBS on Main track unsatisfiable benchmarks}
\end{figure}
\label{main:unsat}

@@

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/parallel-ALL.pdf}
\caption{Performance of the solvers in the Parallel track.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/cloud-ALL.pdf}
\caption{Performance of the solvers in the Cloud track.}
\end{figure}

@@

\section*{Acknowledgements}
Matti J\"arvisalo was financially supported by Academy of Finland grants 322869 and 328718.

Martin Suda was supported by the ERC Consolidator grant AI4REASON no. 649043 under the EU-H2020 programme,
the Czech Science Foundation project 20-06390Y, and the project RICAIP, no. 857306 under the EU-H2020 programme.

Nils Froleyks is supported by the Austrian Science Fund (FWF) under projects
W1255-N23, S11408-N23 and by the LIT AI Lab funded by the State of Upper
Austria.

>>>>

The rest of this article is organized as follows. 
We start by providing an overview on the competition, including details on and motivations for the several
competition tracks, the rules and other technical requirements of the competition, the ranking schemes used
in evaluating the competing solvers, 
and the computing environments used for executing the competition
(Section~\ref{sec:overview}).
We then provide an overview of the benchmark sets used in evaluating the solvers, including their origins and the selection
process used for constructing the sets (Section~\ref{sec:instances}).
In Section~\ref{sec:results} we provide an overview of the competition results together with  a survey on the
the solving strategies implemented distinctly in  top-ranking  solvers. 
Going considerably beyond the plain competition rankings, we provide more in-depth analysis of the competition 
data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
of individual solvers to the ``virtual best solver'' and 
portfolios constructed from the competing solvers,  (Section~\ref{sec:analysis}.
The article is concluded with future prospects in Section~\ref{sec:conclusion}.
\todo{Need to decide on final structure regarding the results overview and analysis}

@@

This section describes some high-level observations, including the winners, of the 2020 SAT Competition. 
We focus on some interesting results. Details about the solvers, including the key and new solving techniques,
are described in Section~\ref{sec:analysis}.

Four solver participating in the Main track (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alliup-trial}, and \solver{CMS-ccnr-lsids}) 
performed significantly better compared to the others, see Table~\ref{tab:results}.
Figure~\ref{main:all} shows the cumulative solved instances plot of the best performing solver of the strongest
10 teams (in short, the top 10 solvers)  together with the Virtual Best Solver (VBS).
The four top solvers all have a different code base, which is rare and has not been observed in many years.
Also, in recent competitions, the top solvers were much closer together.
The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
\solver{Relaxed-newTech} solved more instances within the 2000 seconds limit.
The third place, based on the PAR-2 score, was for \solver{CMS-ccnr-lsids}. It solved two fewer instances
compared to \solver{CaDiCaL-alliup-trial}, but solved various formulas much more efficiently. 
Since the SAT Competition started to rank based on the PAR-2 score, such cases have been observed several times.

\begin{figure}[ht]
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
\label{main:all}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-SAT.pdf}
\caption{Performance of the top 10 solvers + VBS on Main track satisfiable benchmarks}
\label{main:sat}
\end{figure}

The solver performances on unsatisfiable formulas was much closer,
see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
performed significantly better compared to all other participants. It is therefore not surprising
that the VBS is reasonably close to \solver{Kissat-unsat}. \solver{Kissat} is a new solver that has been implemented in C, while most solvers are implemented in C++. Further 
details about \solver{Kissat} are described in Section~\ref{sec:kissat}.
The solvers \solver{CaDiCaL-trial}
and \solver{f2trc-s} won the second, respectively, third place in the Main UNSAT track.

\begin{figure}[ht]
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-UNSAT.pdf}
\caption{Performance of the top 10 solvers + VBS on Main track unsatisfiable benchmarks}
\end{figure}
\label{main:unsat}

The ranking in the Planning Track was closer. \solver{CaDiCaL-alliup-trial}, the winning solver, 
solved only one instance more compared to the runner up \solver{CMS-ccnr-lsids}. Their PAR-2 score is 
quite close as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but fast runtime
on several instances resulted in a strong PAR-2 score. Notice that these solvers were also strong in the Main tracks. 
Apparently none of the participating solvers was optimized for planning instances.

The winning solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. The number in the postfix denotes
that this solver used 32 threads on the 64 virtual cores that were available. It has been observed in earlier 
competitions that uses fewer threads than the number of virtual cores can be helpful as threads compete 
for memory, which can reduce of the overall performance. The runner up is \solver{Plingeling}, while the
third place is for \solver{ManyGlucose-32}. Figure~\ref{fig:res-parallel} shows the performance of
all participating parallel solvers. Notice in Table~\ref{tab:results} that only the \solver{Painless-MCOMSPS-STR} solvers
and \solver{Plingeling} had a lower PAR-2 score than the winner of the Main Track (\solver{Kissat-sat}). 
This shows that it is hard to beat sequential solvers with a parallel solver on the competition instances. 
We will show later in the article (Table~\ref{tab:tuples}) that small sequential portfolios 
perform better (in terms of PAR-2 score) than the parallel solvers.

\begin{figure}[ht]
\centering
\includegraphics[width=.9\textwidth]{img/parallel-ALL.pdf}
\caption{Performance of the solvers in the Parallel track.}
\label{fig:res-parallel}
\end{figure}

The clear winner of the Cloud track is \solver{Mallob-Mono} and the runner-up is \solver{TopoSAT2},
see Figure~\ref{fig:res-cloud}.
\solver{Mallob-Mono} was able to solver more instances in 1000 seconds, compared to the 
winner of the Parallel Track in 5000 seconds, thereby showing the potential of distributed SAT solving. 
The other four participants performed significantly worse. This is likley due to the initial challenges
to develop a distributed solver. This was the first year of this track. We expect that the gap will be 
closer is future years.

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/cloud-ALL.pdf}
\caption{Performance of the solvers in the Cloud track.}
\label{fig:res-cloud}
\end{figure}

@@

@@

@@

\section*{Acknowledgements}
The authors thank StarExec for their support and resources to run the Main and the Planning tracks, and Amazon Web Services 
for their support and resources to run the Parallel and Cloud tracks.

Nils Froleyks is supported by the Austrian Science Fund (FWF) under projects
W1255-N23, S11408-N23 and by the LIT AI Lab funded by the State of Upper
Austria.
%
Marijn Heule is supported by the National Science Foundation (NSF) under grant CCF-2010951. 
%
Matti J\"arvisalo was financially supported by Academy of Finland grants 322869 and 328718.
%
Martin Suda was supported by the ERC Consolidator grant AI4REASON no. 649043 under the EU-H2020 programme,
the Czech Science Foundation project 20-06390Y, and the project RICAIP, no. 857306 under the EU-H2020 programme.
